### 2018-09-18 Writeup/PERT_New.tex
Fixed convexify typos and big-M
Added the header

	\textcolor{blue}{NP-hardness proof. Add the conclusion of consistency. Add the proof of consistency. Prove the inconsistency of the stratified sampling method. }

@@

\section{Experimental Results} \label{sec:results}

\bibliographystyle{plain}
\bibliography{PERT_Bib}

>>>>

	\textcolor{blue}{NP-hardness proof.}
	%Add the conclusion of consistency. Add the proof of consistency. Prove the inconsistency of the stratified sampling method.

@@

\section{Experimental Results} \label{sec:results}
%	\textcolor{blue}{Test results:
%	\begin{itemize}
%		\item Describe the test examples: where do they come from, number of nodes, how are they generated.
%		\item Cite Sen's paper and describe the implementation.
%		\item Results.
%	\end{itemize}}
	In this section, we address the following questions with our computational results:
	\begin{enumerate}
		\item What is the value of model~\eqref{prob:extensive} that takes account of randomness in both timing and magnitude of a disruption? In other words, what are other alternative solutions that are easier to obtain but possibly inferior? How does quality of the solution to model~\eqref{prob:extensive} compare to those alternative solutions?
		\item How does the solution quality improve as the number of samples used in sample average approximation increases? 
		\item What is the time improvement of Algorithm~\ref{alg:Cut} compared to solving extensive formulation~\eqref{prob:extensive} using state-of-the-art MIP solvers? Other algorithms solving 2SMIP with mixed binary recourse?
	\end{enumerate}
	We first introduce the PERT network used for test and distribution information used to characterize uncertainty in Section~\ref{subsec:example}. In Section~\ref{subsec:value} we construct a series of deterministic and semi-deterministic alternatives to model~\eqref{prob:extensive}, perform out-of-sample tests, and present the better quality result of solution to model~\eqref{prob:extensive} compared to the alternative ones. We test the effect of different simulation budgets on solution quality and computational performance in Section~\ref{subsec:budget}. Finally in Section~\ref{subsec:time} we present the computational advantage of Algorithm~\ref{alg:Cut} compared to solving extensive formulation and the ancestral Benders decomposition method (\textcolor{blue}{Cite Sen's two papers}.)\\
	\newline
	All tests are run on a server with 20 Intel Xeon cores at 3.1 GHz and 256 GB of RAM. All models are constructed using version 0.18.0 of the JuMP package \cite{DunningHuchetteLubin2017} on the Julia platform. All linear programs and mixed integer programs are solved by Gurobi 8.01 \cite{gurobi2016} with default parameters.

	\subsection{Test Cases Construction} \label{subsec:example}
	\subsection{Value of a Fully Stochastic Model} \label{subsec:value}
	In this section, we first construct a deterministic problem assuming no disruption occurs and three semi-deterministic alternatives assuming: both timing and magnitude of the disruption are random, only the timing is random, and only the magnitude is random.
	\subsection{Simulation Budget} \label{subsec:budget}
	\subsection{Computational Performance} \label{subsec:time}
\bibliographystyle{plain}
\bibliography{PERT_Bib}
